---
title: "Variable selection in DEA with adea method"
author: 
 - Fernando Fernandez-Palacin^[Universidad de Cádiz, fernando.fernandez@uca.es]
 - Manuel Munoz-Marquez^[Universidad de Cádiz, manuel.munoz@uca.es]
date: "`r Sys.Date()`"
bibliography: dea.bib
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Variable selection in DEA with adea method}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)
library('adea')
```

# Introduction

Variable selection in DEA is a question that requires full attention before the results of an analysis can be used in a real case, because its results can be significantly modified depending on the variables included in the model.
So, variable selection is a keystone step in each DEA application.

`adea` provides a measure called load of the contribution of a variable into a DEA model.
In an ideal case, when all variables contribute in same way, all loads will be 1.
Thus, for example, if an output variable load is 0.75, means that its contribution is 75% of the average value for all outputs. 
A value for variable load lower than 0.6 means that its contribution to DEA model is negligible.

For more information see [@Fernandez2018] and [@Villanueva2021].

Let's load and have a look at the `tokyo_libraries` dataset with
```{r}
data(tokyo_libraries)
head(tokyo_libraries)
```

# Step wise variable selection

Two step wise variable selection functions are provided.
The first one drops variables one by one giving a set of nested models.
The following code setup input and output variables and do the call
```{r}
input <- tokyo_libraries[, 1:4]
output <- tokyo_libraries[, 5:6]
adea_hierarchical(input, output)
```

```{r include=FALSE}
m <- adea_hierarchical(input, output)
```

The load of the first model is `r m$models[[6]]$load$load` which is under the minimum significance level, so `Area.I1` can be removed from the model.

When a variable is removed what one can expect is that the load of all variables raise, but after the second model this not happen.
So third model is poorer than second and there is no statistical reason to select it.

To avoid that a second step wise selection variable is provided, the new call is
```{r}
adea_parametric(input, output)
```

In both case, all variables have been taken into account to remove them, but `load.orientation` parameter allows to select which variables have to be included in load analysis, `input` for only input variables, `output` for only output variables, and `inoutput`, the default value for all variables.
The next call consider only output variables as candidate variables to be removed:
```{r}
adea_parametric(input, output, load.orientation = 'output')
```

`adea_hierarchical` and `adea_parametric` return a list, called `models`, with all computed model that can be accessed through the following call
```{r}
m <- adea_hierarchical(input, output)
m4 <- m$models[[4]]
m4
```
where the number in square brackets is the number of total variables in the model.

By default, when `print` function is called with an `adea` model, it prints only efficiencies.
`summary` results in a wider output:
```{r}
summary(m4)
```


# References