---
title: "Constrained ADEA model"
author: 
 - Fernando Fernandez-Palacin^[Universidad de Cádiz, fernando.fernandez@uca.es]
 - Manuel Munoz-Marquez^[Universidad de Cádiz, manuel.munoz@uca.es]
date: "`r Sys.Date()`"
bibliography: dea.bib
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Constrained ADEA model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)
library('adea')
```

# Introduction

Variable selection in DEA is a question that requires full attention before the results of an analysis can be used in a real case, because its results can be significantly modified depending on the variables included in the model.
So, variable selection is a keystone step in each DEA application.

The selection procedure can lead to remove a variable that decision maker could want to keep a variable in the model for political, tactical or any other reason.
But the contribution of that variable will be negligible if nothing is done.
`cadea` function provides a way force the contribution of a variable to a model be at least a given value.

For more information about loads help of the package about `adea` or see [@Fernandez2018] and [@Villanueva2021].

Let's load and have a look at the `tokyo_libraries` dataset with
```{r}
data(tokyo_libraries)
head(tokyo_libraries)
```

# Constrained ADEA

First of all let's do an `adea` with the following call
```{r}
input <- tokyo_libraries[, 1:4]
output <- tokyo_libraries[, 5:6]
m <- adea(input, output)
summary(m)
```
It shows that `Area.I1` has a load under 0.6, which means its contribution to DEA model is negligible.

With the following call to `cadea` the contribution of `Area.I1` is force to be higher than 0.6:
```{r}
mc <- cadea(input, output, load.min = 0.6, load.max = 4)
summary(mc)
```

Note that the maximum value of a variable load is the maximum number of variables of its types, so `load.max = 4` has no effect on results.

Now load level raises to the given value of 0.6, efficiency average decreases a little.

To compare both efficiency set, observe that Spearman correlation coefficient between them is `r round(cor(m$eff, mc$eff, method = 'spearman'), 4)`.
This can also be seen in the next plot:
```{r echo=FALSE}
plot(m$eff, mc$eff, main ='Initial efficiencies vs constrained model efficiencies')
```

All these mean that in this case the change are small.
Bigger change can be expected if `load.min` grows.

# References